\title{CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by the template
% found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass[paper=letter]{tccv}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[super]{nth}

\begin{document}

\part{Kevin Liu}

% You could put a short summary here!

Version 2020.10

\section{Summary}

Student tech entrepreneur, experienced full-stack programmer with extensive
knowledge of Solidity, React, JavaScript, Java, C\#, Python. Interested in
applying principles of effective altruism to real-world risks.

\section{Work Experience}

\begin{eventlist}

\item{2018 -- Present}
     {Delphus} {Co-founder \& CTO}

    Startup aiming to restore trust and transparency to scientific research.
    \href{https://delph.us}{\textbf{Delphus}}, improves data tracing by
    recording all study actions immutably on an append-only ledger.

\end{eventlist}

\vspace{-0.5cm}
\begin{enumerate}
     \item Directed product development; implemented majority of features in
     20k+ LoC
     \href{https://gitlab.scintillating.us/scintillating/delphus}{open-source
     software}, including end-to-end encrypted chat and data storage on the
     InterPlanetary File System.
     \item 2020 National Science Foundation I-Corps member at Carnegie Mellon
     University.
     \item dlab VC finalist (ranked top 7/200 applicants), Alchemist Accelerator
     finalist (top 1\%).
     \item Presented at the MIT Business Bitcoin Pitch Competition, Babson
     College, HBS Tech Conference and Healthcare Conference 2019/20, MIT
     Enterprise Forum, and Roxbury Innovation Center.
     \item Inventor on utility patent filed in June 2019.
\end{enumerate}

\begin{eventlist}
    \item{2020 -- Present}
         {OpenAI}{Debater (Contract)}

    Part-time honest debater testing OpenAI's
    \href{https://www.alignmentforum.org/posts/Br4xDbYu4Frwrb64a/writeup-progress-on-ai-safety-via-debate-1}{Debate
    Protocol}. Evaluated and provided evidence on conceptual physics and
    mathematical problems to emulate the style of argument of potential future
    AI protocols.
\end{eventlist}

\personal
    [linkedin.com/in/the-kevin-liu] {75 Inches Brook Lane, Boxborough, MA 01719,
    United States} {+1 (781) 315-6703} {kevin@kliu.io} {kliu.io}

\section{Extracurriculars}

\begin{enumerate}
    \item \textbf{2020}: Stanford Effective Altruism, Stanford Existential Risks
    Initiatve -- Exec Member

        Completed Arete Fellowship, weekly reading of effective altruism
        materials and discussion with a mentor group. Currently participating in
        In-Depth Fellowship, a more targeted group for members seeking to
        understand concepts including forecasting, long-term existential risks,
        AI safety.

        Other participation: AI Safety Reading Group, Confusion Dinners,
        Projects Team

    \item \textbf{2020}: Stanford One for the World -- Exec Member

        \href{https://onefortheworld.su.domains}{Designed website} to emphasize
        the impacts of effective altruism on global health and development.
        Executive board member. Aimingto reach majority of undergraduate student
        body this fall.
    \item \textbf{2016-20}: Resource Force
        \begin{itemize}
             \item Created \href{https://gasleaks.info}{gasleaks.info}, a site
             mapping and raising awareness for gas leaks in Acton, MA. Worked in
             conjunction with Mothers Out Front. Presented to Green Advisory
             Board, League of Women Voters, Acton Board of Selectmen; wrote
             comments to DPU.
        \end{itemize}
    
    \item \textbf{2016-20}: AB Robotics Member, Co-Captain
        \begin{itemize}
           \item Helped code and design the autonomous robot control program for
           the Acton Robotics team for the FIRST robotics competition, using
           Java with an Android phone controller, using CV tools and Vuforia.
           \item First alliance pick at Needham Regional Qualifier, semifinalist
           at 2019 MassFTC State Championship.
        \end{itemize}
    \item \textbf{Public-facing homelab}: Bare-metal Kubernetes cluster running
    on NixOS

        Self-learned experience in Linux, enterprise server system
        administration. Proficient with HP iLO, NixOps deployment software.
        Services secured with firewalls and automated Let's Encrypt for HTTPS.
     
\end{enumerate}

See additional projects at \href{https://github.com/kliu128}{github.com/kliu128}
and \href{https://gitlab.kliu.io/kevin}{gitlab.kliu.io/kevin}.
    

\section{Hackathons}

\begin{yearlist}
    \item{Hack3}
         {Co-organizer} {July 2020}

    % 2019-11-08 to 2019-11-10
    \item{ETHWaterloo 2019}
        {Torus, ENS, and NuCypher Sponsor Awards} {Cortex}

    % 2018-03-17 to 2018-03-18
    \item{MIT Bitcoin Expo 2018}
        {\nth{2} Place} {reBlock}

    % 2018-02
    \item{MAHacks III}
        {\nth{1} Place} {reBlock}

    % 2018-09-22
    \item{DoraHacks GHS}
        {\nth{1} Place} {Delphus}

    % 2017-09-30
    \item{LexHack}
        {\nth{2} Place} {Akira}

    % 2017-11-04
    \item{HackNEHS}
        {\nth{3} Place} {Litcoin}

    % 2018-02-18
    \item{MIT Blueprint 2018}
        {\nth{3} Place} {Quecoin}

    % 2017-04-15 https://github.com/stuckathomedev/duck-feed/commits/master
    \item{HackExeter 2017}
        {Developer's Award} {Duck Feed}

    % See https://gitlab.com/stuckathome/production-focus
    \item{HackExeter 2018}
        {\nth{1} Place} {Production Focus}
\end{yearlist}

\subsection{Notable resultant projects}

\textbf{Cortex}\footnote{\url{https://gitlab.scintillating.us/scintillating/cortex}}
-- A social proof, key management, and data authorization platform for Ethereum

\textbf{Delphus
(reBlock)}\footnote{\url{https://gitlab.scintillating.us/scintillating/delphus}}
-- Secure, decentralized, and open scientific study management platform

\textbf{Hack3}\footnote{\url{https://hack3.co}} -- Online hackathon with 200+
participants from dozens of countries. Raised \$2,000 in sponsorship and brought
in speakers from Amazon Web Services, KTBYTE Robotics, and the Stormgear
robotics team. 

\textbf{}

\section{Education}

\begin{yearlist}
     \item{2020-2024}
          {Stanford University} {Computer Science}
     \item{2016-2020}
          {Acton-Boxborough Regional High School} {GPA 4.895}
\end{yearlist}

Current classes: CS103 \textit{Mathematical Foundations of Computing}, CS106B
\textit{Programming Abstractions}.

\section{Programming skills}

\begin{factlist}

\item{Experienced}
     {JavaScript (React, Redux), TypeScript, HTML/CSS, C\#, Python, Java,
     Kotlin, Solidity, \LaTeX}

\item{Basic level}
     {Rust, Bash, Ruby}

\item{Technologies}
     {Kubernetes, Docker, LXC, QEMU/KVM, Ansible; Linux system administration,
     machine learning with Tensorflow}

\end{factlist}

\section{Other skills}

\begin{factlist}

     \item{Languages}
          {English (Native), Spanish (Working)}
     
\end{factlist}

\end{document}
